Arrows for Parallel Computations

### 2017-09-25 paper/content/parallelHaskells.tex
wip on parallelHaskells.tex (added overview table)

\begin{table}[]
\centering
\caption{Overview over some parallel Haskells}
\label{my-label}
\begin{tabular}{\pipe l \pipe l \pipe l \pipe} 
Name		& Memory setting & Concepts used \\
GpH         & shared \& distributed & |par|/|pseq| "hints" \\
|Par| Monad & shared & deterministic parallel Monad \\
Eden        & shared \& distributed & special compiler, pure \& monadic interface \\
HdpH        & \mbcomment{shared?} \& distributed & parallel Monad, Template Haskell \\
LVish       & shared & parallel Monad, parallel data-structures\\
\end{tabular}
\end{table}

>>>>

\parallelHaskellOverview
